\clearpage
\section*{Project Plan}
\phantomsection
\addcontentsline{toc}{section}{Project Plan} 

% =============================================================================
% INTRODUCTION
% =============================================================================
\subsection*{Introduction}
\phantomsection
\addcontentsline{toc}{subsection}{Introduction}

This project aims to build a search engine that allows students to retrieve 
relevant documents from a financial dataset. It is part of an educational 
initiative to promote financial literacy. This enables students to better 
understand and handle real-world financial situations encountered during their 
professional lives. To achieve this goal we have designed and implemented 
an \textit{Information Retrieval (IR)} system that processes textual data, 
builds an \textit{index} over a document collection, and \textit{ranks} 
documents in response to user queries. [1]


% =============================================================================
% TEAM ROLES AND RESPONSIBILITIES 
% =============================================================================
\subsection*{Team Roles and Responsibilities }
\phantomsection
\addcontentsline{toc}{subsection}{Team Roles and Responsibilities}

\textbf{Porter Clevidence} 
\begin{itemize}
    \item   Implemented BIM search 
    \item   Implemented BM25 search 
    \item   Implemented Language Model retrieval
    \item   Implemented VSM search 
    \item   Search algorithm selection
\end{itemize}

\textbf{Antonio Duran-Ramos}
\begin{itemize}
    \item   Development environment setup 
    \item   Graphical interface design 
    \item   Written report [2]
    \item   Figures and Tables
    \item   Dataset statistics
\end{itemize}

\textbf{Parth Gajjar}
\begin{itemize}
    \item   Presented
\end{itemize}

\textbf{Arpit Vora}
\begin{itemize}
    \item   Slideshow presentation 
\end{itemize}


% =============================================================================
% METHODS AND TECHNIQUES 
% =============================================================================
\subsection*{Methods and Techniques}
\phantomsection
\addcontentsline{toc}{subsection}{Methods and Techniques}

To ensure cross-platform reproducibility across all of our team members, 
we used \texttt{Docker} [8] for containerization. Docker allowed us to standardize
our development environment so that our search engine behaved identical, 
regardless of the host machine's underlying operating system. 

Within this Docker container, our project formalizes its Python dependencies 
with \texttt{uv} [9] as the the primary package and virtual environmental manager. 
uv ensured exact reproducibility of the software state for implementation of 
the search engine. 

Within uv, the core retrieval logic and presentation layers are constructed 
with various Python libraries:
\begin{itemize}
    \item   \texttt{pandas} was used to parse the provided JSON dataset files 
            to create structured data frames 
    \item   \texttt{nltk} and \texttt{scikit-learn} were used for natural 
            language processing tasks; \texttt{nltk} for its implementation 
            of the \textit{Porter Stemming} algorithm and \texttt{scikit-learn}
            for its list of English stop words
    \item   \texttt{scikit-learn} was also used for its functions 
            \texttt{TfidfVectorizer} and \texttt{cosine\_similarity}
    \item   \texttt{rank-bm25} was used for its implementation of the BM25 
            ranking algorithm 
    \item   \texttt{streamlit} [3] was used to implement the graphical interface 
            of the search engine 
    \item   \texttt{matplotlib} was used to render figures and graphs based 
            on retrieved data 
\end{itemize}



% =============================================================================
% DATA
% =============================================================================
\subsection*{Data}
\phantomsection
\addcontentsline{toc}{subsection}{Data}

The dataset provided consisted of a collection of financial documents, 
along with static queries and their corresponding relevance judgments.
