\clearpage
\section*{Retrieval Model}
\phantomsection
\addcontentsline{toc}{section}{Retrieval Model}

% ============================================================================ 
% RANKING
% ============================================================================ 
\subsection*{Ranking}
\phantomsection
\addcontentsline{toc}{subsection}{Ranking}

Before any relevance scores can be computed, the system projects the 
preprocessed queries and the document collection into mathematical 
representations. The mathematical representations are dictated by the 
requirements of the active retrieval model. 
\begin{itemize}
    \item   For the Vector Space Model, both the documents and query are 
            represented as high-dimensional, normalized vectors in a 
            shared vocabulary space through the \texttt{TfidfVectorizor}
            function.
    \item   For the BM25 and Language Models, documents and queries are 
            represented as sequential lists of tokens. This list preserves 
            the localized term frequencies and document lengths for 
            probabilistic scoring and unigram or bigram sequences.
    \item   For BIM, documents and queries are mapped to Python's \texttt{set}
            objects. We discard term frequencies and sequence data to 
            evaluate binary term presence.
\end{itemize}

Then, during query execution, the search engine iterates over the document 
space and generates a relevance score for each document. Again, this score 
is dictated by the active retrieval model.
\begin{itemize}
    \item   For Vector Space Model, the system calculates the cosine angle 
            between the query vector and document vectors. This yields a 
            similarity score between $0.0$ and $1.0$. 
    \item   For BM25, the system calculates a score based on term frequency 
            and document length normalization constraints.
    \item   For BIM, the system iterates through the query terms, checking for 
            set intersections with the document. This system dynamically 
            sums the probabilistic weights for all intersecting terms.
    \item   For the Language Models, the system calculates the probability of 
            the query given the document model. This system transforms the 
            smooth probabilities into log space and sums them to prevent 
            arithmetic underflow caused by multiplying small probabilities. 
\end{itemize}

After the relevance scores have been computed across the entire collection, 
the values are stored in a contiguous array, parallel to the original 
document ID index. To establish a final ranking order, the array is sorted 
from highest relevance score to lowest using Python's sorting capabilities. 
The ordered indices, along side their scores, are stored in a data frame 
that is then used for pagination in the graphical interface. 